---
title: "Custom Script Links Placement"
format:  html
extensions:
  ripper:
    include-yaml: true
    script-links-position: custom
    debug: true
filters:
  - ripper
---

## Overview

This document demonstrates the use of the `ripper` extension in a mixed R and Python Quarto document with customized settings.

The document configuration is given as:

````markdown
---
title: "Mixed Language Analysis"
format:
  html:
    keep-md: true
extensions:
  ripper:
    include-yaml: true
    script-links-position: custom
    
    debug: true
filters:
  - ripper
---
````

The settings specify that the extracted scripts should include YAML headers and that the links to the scripts should be placed at a custom location within the document by creating a div with the id `#ripper-links`.

e.g.

```markdown
:::{#ripper-links}
:::
```

This div will be replaced by the `ripper` extension with links to the generated script files, which we can see below.

----

:::{#ripper-links}
:::

----

The remaining sections contain code blocks in R and Python that will be extracted by the `ripper` extension.

## R Analysis

This section demonstrates R code for data analysis.

```{r}
#| label: r-analysis
data <- mtcars
summary(data)
```

## Python Analysis

This section shows Python code for data manipulation.

```{python}
#| label: python-analysis
dictionary = {"x": [1, 2, 3], "y": [4, 5, 6]}
print(dictionary.keys())
```

## More R Code

Additional R code for plotting.

```{r}
#| label: r-plotting
#| echo: false
plot(mtcars$mpg, mtcars$hp)
```
